% Physics 206L
% 2015 Fall semester
% Mid-term
% Author: Randy P. Tompkins
% 200 points possible


\documentclass[12pt]{article}
\usepackage{fullpage}
\usepackage{circuitikz}


\begin{document}

\title{Comments On Midterm Examination}
\author{Dr. Randy P. Tompkins}
\date{October 17, 2015}

\maketitle

\noindent
Class average was a 61\%.


\begin{enumerate}

\item{Both accuracy can precision were stressed in lecture and multiple laboratory assignments.} 
\item{Computed in muliple laboratory assignments.}
\item{Taken exactly from the prelab section of the speed of sound lab.}
\item{Taken exactly from the prelab section of the speed of sound lab.}
\item{Stressed in lecture during electric field laboratory. This is a basic question and should not have given people difficulty.}
\item{Taken from Ohm's law pre-lab with numbers changed.}
\item{Variation from question in Ohm's law pre-lab.} 
\item{Similar problems were asked in the excel lab.}
\item{True-False questions came from basic concepts in class and assignments. These questions were not difficult.}
\item{Basic questions about RC circuits. Time constant was computed in prelab.}
\item{Variation to homework problem given in class. HW problem was for a dipole, one positive and one negative charge. Test question was two positive charges.}
\item{Combination of resistors in series and parallel. Discussed in lecture and computed in Ohm's law prelab.}
\item{Most missed question on exam. Basic questions on RC circuits. Time constant was a question in prelab. Most did not know maximum charge. This concept was stressed in lecture and is discussed in the textbook. Part 3 was a basic calculation using equation for q(t).}
     
\end{enumerate}


\end{document}



